Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations

### 2019-05-01 tex/cover-letter/cover_letter.tex
Ticking off more things..

\begin{letter}{Editor of Environmental Science \& Technology \\
1155 Sixteenth Street N.W. \\
Washington, DC 20036}
\opening{Dear Sir or Madam:}

I am pleased to submit this manuscript entitled "Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations" for review and possible publication in Environmental Science \& Technology.
This is original work, and has not been previously submitted to any other journal or conference proceedings.

@@

We found under which conditions one may expect to observe significant changes in indoor air concentrations, and when one should be especially be concerned with preferential pathways.
Furthermore, we found how changes in indoor outdoor pressure difference and air exchange rate independently affect temporal variability in VI under different conditions. 
These finding help understand and explain the temporal variation that has been observed at many VI sites, and giving practical guidance for assessment of these sites, something that we expect will be of great interest to your readership.

All of the work presented is either created by us or properly referenced, including the TOC art which adhere to the TOC art policy and is the prescribed size of 240 by 135 points.

>>>>

\begin{letter}{Editorial Department of Building and Environment}
\opening{Dear Sir or Madam:}

I am pleased to submit this manuscript entitled "Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations" for review and possible publication in Building and Environment.
This is original work, and has not been previously published by any other journal or conference proceedings.

@@

Some of our conclusions that we believe contribute to the state-of-the-art:
\begin{itemize}
  \item Preferential pathways may lead to the false conclusion that there are indoor sources present at a VI site.
  \item Preferential pathways can dramatically increase a VI site's sensitivity to building pressurization.
  \item Air exchange rate is poorly correlated with normal range of building pressurization and may significantly contribute to indoor contaminant variability.
  \item Indoor contaminant concentration vary roughly by up to a factor of two across a few days; up to an order magnitude variation may be expected over a week.
\end{itemize}
We expect the topics explored and conclusions reached in our work will be of great interest to your readership.

### 2019-05-01 tex/main.tex
Ticking off more things..

% keywords
%\abbreviations{VI}
%\keywords{}

\journal{Building \& Environment}

@@

\begin{abstract}
Temporal variability in indoor air contaminant concentrations at vapor intrusion (VI) sites has been a concern for some time.
We consider the source of the reported variability at VI sites located near Hill Air Force Base (AFB) in Utah, an EPA experimental house in Indiana, and Naval Air Station North Island in California.
We focus in particular on how the indoor/outdoor pressure differences and air exchange rates affected indoor air contaminant concentrations at these sites.
We investigate how these dynamics differ for a site that is characterized by a preferential pathway (like Hill AFB) and VI sites that are not influenced by such pathways, using three-dimensional fluid dynamics models and statistical analysis of the aforementioned sites.
For a preferential pathway to impact a VI site, there must exist a medium allowing effective communication between a contaminant-delivering preferential pathway and the indoor air space, e.g. a permeable subslab space that may be provided by a gravel layer.
At sites characterized by significant advective transport from the subslab to the indoor air space, much of the short-term variability in indoor air contaminant concentration can be explained by an impact of fluctuations in indoor/outdoor pressure differences.
Meanwhile, air exchange rate variation drives most of the short-term variability at sites characterized by minor variations in advective transport.
\end{abstract}

\begin{keyword}
  Vapor intrusion \sep Preferential pathways \sep Temporal variability \sep Finite element modeling \sep Air exchange rate \sep Indoor/outdoor pressure difference
\end{keyword}

@@

\section{Methods}

\subsection{Statistical Analysis Of Field Data}

@@

\begin{figure}
  \centering
 \includegraphics[width=\textwidth]{time_indianapolis.pdf}
 \caption{Typical data on indoor air TCE contaminant concentrations at the Indianapolis site\cite{u.s._environmental_protection_agency_assessment_2015}.}\label{fig:indianapolis}
\end{figure}

@@

\subsection{Modeling Work}

@@

% new table
% TODO: Fix the too wide issue
\clearpage
\begin{table}
  \centering
  \begin{tabular}{l c c c c c c}
    \toprule
    \multicolumn{7}{c}{\textbf{Governing Equations}} \\
    \midrule
    % CSTR
    Unsteady-CST & \multicolumn{6}{c}{$V\frac{d c_\mathrm{in}}{d t} = \int_{A_\mathrm{ck}} j_\mathrm{ck} dA - c_\mathrm{in} A_e V_\mathrm{slab}$} \\
    % RICHARDS
    Richard's & \multicolumn{6}{c}{$\nabla \cdot \rho \Big( - \frac{\kappa_s}{\mu} k_r \nabla p \Big) = 0$} \\
    % TRANSPORT
    Transport & \multicolumn{6}{c}{$\frac{\partial}{\partial t} \Big( \theta_w c_w + \theta_g c \Big) = \nabla (D_\mathrm{eff} \cdot \nabla c) - \vec{u} \cdot \nabla c$} \\
    % MILLINGTON-QUIRK
    Millington-Quirk & \multicolumn{6}{c}{$D_\mathrm{eff} = D_\mathrm{air}\frac{\theta_g^{10/3}}{\theta_t^2} + \frac{D_\mathrm{water}}{K_H} \frac{\theta_w^{10/3}}{\theta_t^2}$} \\
    % VAN GENUCHTEN
    \multirow{4}{*}{van Genuchten's} & \multicolumn{6}{c}{$\mathrm{Se} = \frac{\theta_w - \theta_r}{\theta_t - \theta_r} = [1 + |\alpha z|^n]^{-m}$} \\
     & \multicolumn{6}{c}{$\theta_g = \theta_t - \theta_w$}\\
     & \multicolumn{6}{c}{$k_r = (1-\mathrm{Se})^{l}[1(\mathrm{Se}^{m})^m]^2$} \\
     & \multicolumn{6}{c}{$m = 1 - 1/n$} \\
    \midrule
    \multicolumn{7}{c}{\textbf{Boundary Conditions}} \\
    \midrule
    \textbf{Boundary} & \multicolumn{3}{c}{\textbf{Richard's Eqn.}} & \multicolumn{3}{c}{\textbf{Transport Eqn.}} \\
    % Foundation crack
    Foundation crack & \multicolumn{3}{c}{$p = p_\mathrm{in/out} \; \mathrm{(Pa)}$} & \multicolumn{3}{c}{$j_\mathrm{ck} = \frac{u c}{1 - \exp{(u L_\mathrm{slab}/D_\mathrm{air})}}$} \\
    % Groundwater source
    Groundwater & \multicolumn{3}{c}{\textit{No flow}} & \multicolumn{3}{c}{$c = c_\mathrm{gw} K_H \; \mathrm{(\mu g/m^3)}$} \\
    % Ground surface
    Groundsurface & \multicolumn{3}{c}{$p = 0 \; \mathrm{(Pa)}$} & \multicolumn{3}{c}{$c = 0 \; \mathrm{(\mu g/m^3)}$} \\
    % Preferential pathway
    Preferential & \multicolumn{3}{c}{$p = 0 \; \mathrm{(Pa)}$} & \multicolumn{3}{c}{$c = c_\mathrm{gw} K_H \chi \; \mathrm{(\mu g/m^3)}$} \\
    \midrule
    \multicolumn{7}{c}{\textbf{Soil \& gravel properties}\cite{dan_capillary_2012,abreu_conceptual_2012,u.s._environmental_protection_agency_userss_2004}} \\
    \midrule
    \textbf{Soil} & \textbf{$\kappa_s \; \mathrm{(m^2)}$} & \textbf{$\rho \; \mathrm{(kg/m^3)}$} & \textbf{$\theta_s$} & \textbf{$\theta_r$} & \textbf{$\alpha \; \mathrm{(1/m)}$} & \textbf{$n$} \\
    % GRAVEL
    Gravel & $1.3 \cdot 10^{-9}$ & 1680 & 0.42 & 0.005 & 100 & 3.1 \\
    % SANDY LOAM
    Sandy Loam & $5.9 \cdot 10^{-13}$ & 1460 & 0.39 & 0.039 & 2.7 & 1.4 \\
    \midrule
    \multicolumn{7}{c}{\textbf{Building Properties}} \\
    \midrule
     & \textbf{$V_\mathrm{base} \; \mathrm{(m^3)}$} & \textbf{$L_\mathrm{slab} \; \mathrm{(cm)}$} & \textbf{$A_e \; \mathrm{(1/hr)}$} \\
     & 300 & 15 & 0.5 \\
    \bottomrule
  \end{tabular}
  \caption{Governing equations, boundary conditions \& model input parameters. (See below for table of nomenclature).}\label{tbl:eqns_bc_parameters}
\end{table}

\begin{comment}
\clearpage

@@

@@

 \bigskip
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Governing equations
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subcaption{Governing equations}
 \begin{tabular}{l l}

@@

  % Indoor air space equation
  Unsteady-CST                            &                                                                   \\
  % Richard's equation
  Richard's equation                       & $\nabla \cdot \rho \Big( - \frac{\kappa_s}{\mu} k_r \nabla p \Big) = 0$                                                               \\
  % Millington-Quirk equation
  Millington-Quirk                         & $D_\mathrm{eff} = D_\mathrm{air}\frac{\theta_g^{10/3}}{\theta_t^2} + \frac{D_\mathrm{water}}{K_H} \frac{\theta_w^{10/3}}{\theta_t^2}$ \\
  % Advection-diffusion equation
  Advection-diffusion equation             & $\frac{\partial}{\partial t} \Big( \theta_w c_w + \theta_g c \Big) = \nabla (D_\mathrm{eff} \cdot \nabla c) - \vec{u} \cdot \nabla c$ \\
  % van Genuchten's equations
  \multirow{3}{*}{van Genuchten equations} & $\mathrm{Se} = \frac{\theta_w - \theta_r}{\theta_t - \theta_r} = [1 + |\alpha z|^n]^{-m}$                                             \\
                                           & $\theta_g = \theta_t - \theta_w$                                                                                                      \\
                                           & $k_r = (1 - \mathrm{Se})^{l} [1 - (\mathrm{Se}^{-m})^m]^2$                                                                            \\
                                           & $m = 1 - 1/n$                                                                                                                         \\

@@

 \bigskip
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Boundary conditions
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subcaption{Boundary conditions}
 \begin{tabular}{l l l}
  \textbf{Boundary}            & \textbf{Richard's equation}              & \textbf{Transport equation}                                      \\
  Foundation crack          & $p = p_\mathrm{in/out} \; \mathrm{(Pa)}$ & $j_\mathrm{ck} = \frac{u c}{1 - \exp{(u L_\mathrm{slab}/D_\mathrm{air})}}$ \\
  Groundwater source        & \textit{No flow}                                      & $c = c_\mathrm{gw} K_H \; \mathrm{(\mu g/m^3)}$                            \\
  Groundsurface            & $p = 0 \; \mathrm{(Pa)}$                 & $c = 0 \; \mathrm{(\mu g/m^3)}$                                            \\
  Preferential pathway & $p = 0 \; \mathrm{(Pa)}$                 & $c = c_\mathrm{gw} K_H \chi \; \mathrm{(\mu g/m^3)}$                       \\
 \bigskip
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Soil input parameters
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subcaption{Soil \& gravel properties\cite{dan_capillary_2012,abreu_conceptual_2012,u.s._environmental_protection_agency_userss_2004}}
 \begin{tabular}{l l l l l l l}
  % Descriptions
  Soil       & $\kappa_s \; \mathrm{(m^2)}$ & $\rho \; \mathrm{(kg/m^3)}$ & $\theta_s$ & $\theta_r$ & $\alpha \; \mathrm{(1/m)}$ & $n$ \\
  % Gravel
  Gravel     & $1.3 \cdot 10^{-9}$                     & 1680                                    & 0.42       & 0.005      & 100                        & 3.1 \\
  % sandy loam
  Sandy Loam & $5.9 \cdot 10^{-13}$                    & 1460                                    & 0.39       & 0.039      & 2.7                        & 1.4 \\
 \bigskip
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % TCE input parameters
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subcaption{Trichloroethylene (diluted in air) properties\cite{abreu_conceptual_2012,u.s._environmental_protection_agency_userss_2004}}
 \begin{tabular}{l l l l l l}
  $D_\mathrm{air} \; \mathrm{(m^2/h)}$ & $D_\mathrm{water} \; \mathrm{(m^2/h)}$ & $\rho \; \mathrm{(kg/m^3)}$ & $\mu \; \mathrm{(Pa \cdot s)}$ & $K_H$ & $M \; \mathrm{(g/mol)}$ \\
  $2.47 \cdot 10^{-2}$                 & $3.67 \cdot 10^{-6}$                   & 1.614                                   & $1.86 \cdot 10^{-5}$                          & 0.403 & 131.39                  \\
 \bigskip
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Building input parameters
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subcaption{Building properties}
 \begin{tabular}{l l l}
  $V_\mathrm{base} \; \mathrm{(m^3)}$ & $L_\mathrm{slab} \; \mathrm{(cm)}$ & $A_e \; \mathrm{(1/hr)}$ \\
  %
  300                                 & 15                                 & 0.5                      \\

\end{table}
\end{comment}

% TODO: Restructure entire table

\section{Results \& Discussion}\label{s:results}

@@

\subsection{Modeling Results}\label{s:results_modeling}

\subsubsection{Pressure Effects}\label{s:results_modeling_pressure}

@@

\subsubsection{Air Exchange Rate Effects}\label{s:results_modeling_air_exchange}

Table \ref{tbl:air_exchange_rate} shows the observed variations in air exchange rates for the ASU House and Indianapolis House, compared with EPA’s summary of the distribution of typical residential air exchange rates\cite{u.s._epa_exposure_2011,m._d._koontz_estimation_1995}.
Examination of these distributions point in a clear direction for modifying the above model.
Instead of using a constant value of air exchange rate, as is customary, its values should be parameterized.
A higher air exchange would of course be associated with lower $c_\mathrm{in}$ and vice versa.
Moreover, $A_e$ may sometimes be correlated with $p_\mathrm{in/out}$.
Determining any general relationship between $A_e$ and $p_\mathrm{in/out}$ is difficult: the structure itself and weather phenomena have a significant effect on air exchange.
As the data in the supplementary data show (Figure S1), there is no easily discernable correlation between these variables at the ASU site, though there is a hint of slight seasonal dependence.
Note: a relationship between $A_e$ and $p_\mathrm{in/out}$ may be established for larger $p_\mathrm{in/out}$ via the building leakage curves, which are widely used for heating, ventilation and air conditioning systems in construction.\par

@@

\appendix

\clearpage
\begin{table}[htb!]
  \caption{List of abbreviations}\label{tbl:abbreviations}
\begin{tabular}{l l}
  \toprule
  % A/ALPHA
  $A_\mathrm{ck}$ & Crack area \\
  $A_e$ & Air exchange rate \\
  $\alpha, \; n, \; m, \; l$ & van Genuchten parameters \\
  $\alpha_\mathrm{gw}$ & Attenuation from groundwater contaminant vapor source \\
  % C
  $c_\mathrm{in}$ & Indoor air contaminant concentration \\
  $c$ & Soil-gas contaminant concentration \\
  $c_w$ & Soil-water contaminant concentration \\
  $c_\mathrm{gw}$ & Contaminant groundwater concentration \\
  $\chi$ & PP contaminant concentration scaling parameter \\
  % D
  $D_\mathrm{eff}$ & Effective diffusion coefficient \\
  $D_\mathrm{air}$ & Diffusion coefficient in air \\
  $D_\mathrm{water}$ & Diffusion coefficient in water \\
  % J
  $j_\mathrm{ck}$ & Contaminant molar flux through the foundation crack \\
  % K
  $\kappa_s$ & Saturated soil permeability \\
  $K_H$ & Dimensionless Henry's law constant \\
  $k_r$ & Relative permeability \\
  % L
  $L_\mathrm{slab}$ & Thickness of the foundation slab \\
  % M
  $M$ & Molar mass \\
  $\mu$ & Contaminant vapor viscosity \\
  % N
  NAS & Naval Air Stations \\
  % P
  $p$ & Pressure in soil \\
  $p_\mathrm{in/out}$ & Indoor/outdoor pressure difference \\
  PP & Preferential pathway \\
  % R
  $\rho$ & Density \\
  % S
  $\mathrm{Se}$ & Soil water saturation \\
  % T
  $t$ & time \\
  $\theta_g$ & Vapor/gas filled porosity \\
  $\theta_w$ & Water filled porosity \\
  $\theta_r$ & Residual water filled porosity \\
  $\theta_t$ & Total porosity \\
  % U
  $\vec{u}$ & Soil-gas velocity (vector quantity) \\
  % V
  VI & Vapor intrusion \\
  $V_\mathrm{base}$ & Basement volume \\
  % Z
  $z$ & Elevation above groundwater \\
  \bottomrule
\end{tabular}
\end{table}

>>>>

\journal{Building and Environment}

@@

\begin{abstract}
Temporal variability in indoor air contaminant concentrations at vapor intrusion (VI) sites has been a concern for some time.
We consider the source of the reported variability at VI sites located near Hill Air Force Base (AFB) in Utah, an EPA experimental house in Indiana, and Naval Air Station North Island in California.
We focus in particular on how the indoor/outdoor pressure differences and air exchange rates affected indoor air contaminant concentrations at these sites.
We investigate how these dynamics differ for a site that is characterized by a preferential pathway (like Hill AFB) and VI sites that are not influenced by such pathways, using three-dimensional fluid dynamics models and statistical analysis of the aforementioned sites.
A preferential pathway can dramatically increase a VI site's sensitivity to build pressurization, provided there exist a medium allowing effective communication between a contaminant-delivering preferential pathway and the indoor air space, e.g. a permeable subslab space that may be provided by a gravel layer.
Preferential pathways may also erroneously indicate the presence of indoor contaminant sources.
At sites characterized by significant advective transport from the subslab to the indoor air space, much of the short-term variability in indoor air contaminant concentration can be explained by an impact of fluctuations in indoor/outdoor pressure differences.
Meanwhile, air exchange rate variation drives most of the short-term variability at sites characterized by minor variations in advective transport.
\end{abstract}

\begin{keyword}
  Vapor intrusion \sep Preferential pathways \sep Temporal variability \sep Attenuation factor \sep Air exchange rate \sep Indoor/outdoor pressure difference
\end{keyword}

@@

\section{Methods}\label{s:methods}

\subsection{Statistical Analysis Of Field Data}\label{s:methods_stats}

@@

\begin{figure}[htb!]
  \centering
 \includegraphics[width=\textwidth]{time_indianapolis.pdf}
 \caption{Typical data on indoor air TCE contaminant concentrations at the Indianapolis site\cite{u.s._environmental_protection_agency_assessment_2015}.}\label{fig:indianapolis}
\end{figure}

@@

\subsection{Modeling Work}\label{s:methods_model}

@@

@@

  \setlength{\tabcolsep}{1pt}

@@

  \begin{tabular}{l c c c c c c}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % GOVERNING EQUATIONS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \multicolumn{7}{c}{\textbf{Governing Equations}} \\
    \midrule
    % CSTR
    Unsteady-CST & \multicolumn{6}{c}{$V\frac{d c_\mathrm{in}}{d t} = \int_{A_\mathrm{ck}} j_\mathrm{ck} dA - c_\mathrm{in} A_e V_\mathrm{slab}$} \\
    % RICHARDS
    Richard's & \multicolumn{6}{c}{$\nabla \cdot \rho \Big( - \frac{\kappa_s}{\mu} k_r \nabla p \Big) = 0$} \\
    % TRANSPORT
    Transport & \multicolumn{6}{c}{$\frac{\partial}{\partial t} \Big( \theta_w c_w + \theta_g c \Big) = \nabla (D_\mathrm{eff} \cdot \nabla c) - \vec{u} \cdot \nabla c$} \\
    % MILLINGTON-QUIRK
    Millington-Quirk & \multicolumn{6}{c}{$D_\mathrm{eff} = D_\mathrm{air}\frac{\theta_g^{10/3}}{\theta_t^2} + \frac{D_\mathrm{water}}{K_H} \frac{\theta_w^{10/3}}{\theta_t^2}$} \\
    % VAN GENUCHTEN
    \multirow{4}{*}{van Genuchten} & \multicolumn{6}{c}{$\mathrm{Se} = \frac{\theta_w - \theta_r}{\theta_t - \theta_r} = [1 + |\alpha z|^n]^{-m}$} \\
     & \multicolumn{6}{c}{$\theta_g = \theta_t - \theta_w$}\\
     & \multicolumn{6}{c}{$k_r = (1-\mathrm{Se})^{l}[1(\mathrm{Se}^{m})^m]^2$} \\
     & \multicolumn{6}{c}{$m = 1 - 1/n$} \\
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     % BOUNDARY CONDITIONS
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \midrule
    \multicolumn{7}{c}{\textbf{Boundary Conditions}} \\
    \midrule
    \textbf{Boundary} & \multicolumn{3}{c}{\textbf{Richard's Eqn.}} & \multicolumn{3}{c}{\textbf{Transport Eqn.}} \\
    Foundation crack & \multicolumn{3}{c}{$p = p_\mathrm{in/out} \; \mathrm{(Pa)}$} & \multicolumn{3}{c}{$j_\mathrm{ck} = \frac{u c}{1 - \exp{(u L_\mathrm{slab}/D_\mathrm{air})}}$} \\
    Groundwater & \multicolumn{3}{c}{\textit{No flow}} & \multicolumn{3}{c}{$c = c_\mathrm{gw} K_H \; \mathrm{(\mu g/m^3)}$} \\
    Ground surface & \multicolumn{3}{c}{$p = 0 \; \mathrm{(Pa)}$} & \multicolumn{3}{c}{$c = 0 \; \mathrm{(\mu g/m^3)}$} \\
    \multirow{2}{*}{\begin{minipage}{0.2\textwidth}Preferential\\pathway\end{minipage}} & \multicolumn{3}{c}{\multirow{2}{*}{$p = 0 \; \mathrm{(Pa)}$}} & \multicolumn{3}{c}{\multirow{2}{*}{$c = c_\mathrm{gw} K_H \chi \; \mathrm{(\mu g/m^3)}$}} \\ \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % SOIL PROPERTIES
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \midrule
    \multicolumn{7}{c}{\textbf{Soil Properties}\cite{dan_capillary_2012,abreu_conceptual_2012,u.s._environmental_protection_agency_userss_2004}} \\
    \midrule
    \textbf{Soil} & \textbf{$\kappa_s \; \mathrm{(m^2)}$} & \textbf{$\theta_s$} & \textbf{$\theta_r$} & \textbf{$\alpha \; \mathrm{(1/m)}$} & \textbf{$n$} \\
    % GRAVEL
    Gravel & $1.3 \cdot 10^{-9}$ & 0.42 & 0.005 & 100 & 3.1 \\
    % SANDY LOAM
    Sandy Loam & $5.9 \cdot 10^{-13}$ & 0.39 & 0.039 & 2.7 & 1.4 \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % TCE PROPERTIES
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \midrule
    \multicolumn{7}{c}{\textbf{Trichloroethylene (diluted in air) Properties}\cite{abreu_conceptual_2012,u.s._environmental_protection_agency_userss_2004}} \\
    \midrule
     & \multicolumn{1}{c}{\textbf{$D_\mathrm{air} \; \mathrm{(m^2/h)}$}} & \textbf{$D_\mathrm{water} \; \mathrm{(m^2/h)}$} & \textbf{$\rho \; \mathrm{(kg/m^3)}$} & \textbf{$\mu \; \mathrm{(Pa \cdot s)}$} & \textbf{$K_H$} \\
     & \multicolumn{1}{c}{$2.47 \cdot 10^{-2}$} & $3.67 \cdot 10^{-6}$ & 1.614 & $1.86 \cdot 10^{-5}$ & 0.403 \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % BUILDING PROPERTIES
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \midrule
    \multicolumn{7}{c}{\textbf{Building Properties}} \\
    \midrule
     & \multicolumn{1}{c}{\textbf{$V_\mathrm{base} \; \mathrm{(m^3)}$}} & \textbf{$L_\mathrm{slab} \; \mathrm{(cm)}$} & \textbf{$A_e \; \mathrm{(1/hr)}$} \\
     & \multicolumn{1}{c}{300} & 15 & 0.5 \\

@@

  \caption{Governing equations, boundary conditions \& model input parameters. (See below for table of nomenclature).}\label{tbl:eqns_bc_parameters}
\end{table}

\newpage
\section{Results \& Discussion}\label{s:results}

@@

\subsection{Modeling Results}\label{s:results_model}

\subsubsection{Pressure Effects}\label{s:results_model_pressure}

@@

\subsubsection{Air Exchange Rate Effects}\label{s:results_model_air_exchange}

Table \ref{tbl:air_exchange_rate} shows the observed variations in air exchange rates for the ASU House and Indianapolis House, compared with EPA’s summary of the distribution of typical residential air exchange rates\cite{u.s._epa_exposure_2011,m._d._koontz_estimation_1995}.
Examination of these distributions point in a clear direction for modifying the above model.
Instead of using a constant value of air exchange rate, as is customary, its values should be parameterized.
A higher air exchange would of course be associated with lower $c_\mathrm{in}$ and vice versa.
Moreover, $A_e$ may sometimes be correlated with $p_\mathrm{in/out}$.
Determining any general relationship between $A_e$ and $p_\mathrm{in/out}$ is difficult: the structure itself and weather phenomena have a significant effect on air exchange.
As the data in Figure \ref{fig:air_exchange_rate} show, there is no easily discernable correlation between these variables at the ASU site, though there is a hint of slight seasonal dependence.
Note: a relationship between $A_e$ and $p_\mathrm{in/out}$ may be established for larger $p_\mathrm{in/out}$ via the building leakage curves, which are widely used for heating, ventilation and air conditioning systems in construction.\par

\begin{figure}[htb!]
  \includegraphics[width=\textwidth]{pressure_air_exchange_rate.pdf}
  \caption{2D KDE figure showing distributions and relationship between indoor/outdoor pressure difference and air exchange rate. The seasonal median $p_\mathrm{in/out}$ and $A_e$ are indicated by the location of the respective arrow tips. Only non-CPM period considered.}\label{fig:air_exchange_rate}
\end{figure}

@@

\clearpage
\begin{table}[htb!]
  \centering
  \begin{tabular}{l l}
    \toprule
    % A/ALPHA
    $A_\mathrm{ck}$ & Crack area \\
    $A_e$ & Air exchange rate \\
    $\alpha, \; n, \; m, \; l$ & van Genuchten parameters \\
    $\alpha_\mathrm{gw}$ & Attenuation from groundwater contaminant vapor source \\
    % C
    $c_\mathrm{in}$ & Indoor air contaminant concentration \\
    $c$ & Soil-gas contaminant concentration \\
    $c_w$ & Soil-water contaminant concentration \\
    $c_\mathrm{gw}$ & Contaminant groundwater concentration \\
    $\chi$ & PP contaminant concentration scaling parameter \\
    % D
    $D_\mathrm{eff}$ & Effective diffusion coefficient \\
    $D_\mathrm{air}$ & Diffusion coefficient in air \\
    $D_\mathrm{water}$ & Diffusion coefficient in water \\
    % J
    $j_\mathrm{ck}$ & Contaminant molar flux through the foundation crack \\
    % K
    $\kappa_s$ & Saturated soil permeability \\
    $K_H$ & Dimensionless Henry's law constant \\
    $k_r$ & Relative permeability \\
    % L
    $L_\mathrm{slab}$ & Thickness of the foundation slab \\
    % M
    $M$ & Molar mass \\
    $\mu$ & Contaminant vapor viscosity \\
    % N
    NAS & Naval Air Stations \\
    % P
    $p$ & Pressure in soil \\
    $p_\mathrm{in/out}$ & Indoor/outdoor pressure difference \\
    PP & Preferential pathway \\
    % R
    $\rho$ & Density \\
    % S
    $\mathrm{Se}$ & Soil water saturation \\
    % T
    $t$ & time \\
    $\theta_g$ & Vapor/gas filled porosity \\
    $\theta_w$ & Water filled porosity \\
    $\theta_r$ & Residual water filled porosity \\
    $\theta_t$ & Total porosity \\
    % U
    $\vec{u}$ & Soil-gas velocity (vector quantity) \\
    % V
    VI & Vapor intrusion \\
    $V_\mathrm{base}$ & Basement volume \\
    % Z
    $z$ & Elevation above groundwater \\
    \bottomrule
  \end{tabular}
  \caption{List of abbreviations and nomenclature}\label{tbl:abbreviations}
\end{table}
